Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-24 paper/ms.tex
update manuscript

Section~\ref{sec:observations} describes the identification of the
candidate, and the follow-up observations collected.
Section~\ref{sec:validation} combines these data to assess the
system's false positive probability, and finds that \pn\ is almost
certainly a planet.  Section~\ref{sec:system} presents our knowledge
of the cluster (Section~\ref{subsec:cluster}), the star
(Section~\ref{subsec:star}) and the planet
(Section~\ref{subsec:planet}).  We conclude by discussing avenues for
improved characterization in Section~\ref{sec:discussion}.

@@

\paragraph{Acquisition}
We observed four transits with the 0.36m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

{\bf Phil + Karen TODO: please correct as appropriate}
We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
The photometric data were calibrated and extracted using the
\texttt{AstroImageJ} software package
\citep{collins_astroimagej_2017}.  Comparison stars of similar
brightness were used to produce the final light curves, each of which
showed a roughly 4$\,$ppt dip near the expected transit time.
We produced and examined light curves with at custom positions and
with custom aperture sizes, and...

The data were reduced using... (e.g., astroimageJ)

%TODO TODO
% See "TOI-837 : a planet!" thread, May 2020
\paragraph{Custom aperture analysis}
{\bf LGB TODO: Describe custom analysis of apertures. }
"""
While ``Star A'' was detected in the SOAR images, our ground-based
photometry rules it out as a possible source of the eclipse signal
(Section~\ref{subsec:groundphot}).
"""

A total eclipse of Star A would produce a 1.4\%
dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
dips of exactly the right depth (0.4\%).

To assess this possibility with the ground-based photometry, we
produced light curves centered on \tn\ with
circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
We did not detect any statistically significant variation in the depth
of the transits.

We also created light curves with a custom set of $r=2.1''$ apertures
with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
east of \tn.  We did not detect any variation of the transit depth
along this line of light curves, as would be expected if Star A were
the eclipse host.  The apertures east of \tn\ are particularly
constraining, as they exclude over 90\% of the flux from Star A.
The eclipse on Star A would therefore need to be excessively deep to
produce the observed eclipse depth.
We take this to indicate that \tn\ is the source of the transit signal
to within $\approx2.0''$.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		\label{fig:fpscenario}
	}
\end{figure*}

``Validating'' a transiting planet means statistically arguing that
the data are much more likely to be caused by a planet than by other
astrophysical false positives.  The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the data must be explained by a planet, for instance through
combined transits and a mass measurement.

Assuming the eclipse has been localized to the target star within the
available angular resolution, potential false positive scenarios
include eclipses of a background binary (BEB), eclipses of a
hierarchical companion to the primary star (HEB), and the possibility
that the eclipses of \tn\ are simply caused by a stellar companion,
rather than a planetary one (EB).

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
We proceed by describing each constraint in detail, and then present a
statistical calculation using \texttt{VESPA}
\citep{morton_efficient_2012} to demonstrate that the probability \tn\
is an astrophysical false positive is small enough to consider it
``validated''.

\subsection{Constraints on False Positive Scenarios}

@@

Typically, the shape of the transits enables this argument to be
scaled to even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
However, since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

\subsubsection{Speckle Imaging}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
putative bound companions, we opted to employ the
\citet{baraffe_evolutionary_2003} models for substellar mass objects
and the MIST isochrones for stellar mass objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, to ensure that companions
would be at a plausible state of contraction.

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
assumed that all soruces had blackbody spectra.  While this is clearly
a simplification, the custom instrumental bandpasses prevented a fully
consistent stellar evolutionary calculation.  Using the theoretical
stellar parameters and the measured transmission functions
\citep{tokovinin_ten_2018}, we then calculated the apparent magnitude
of putative stellar companions of different masses, and interpolated
to produce the scale shown on the right in
Figure~\ref{fig:fpscenario}.

@@

HEB and to a lesser extent BEB scenarios can be limited
by color photometry.
In the absense of color photometry, the most plausible HEB scenarios for TOI
837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
These eclipses are redder than eclipses of the G-dwarf \tn.
Observations that the transit depth does not decrease
going to blue bands therefore limits the plausibility of these scenarios.

@@

The ``Gaia'' curve in Figure~\ref{fig:fpscenarios} combines both
point-source detections from imaging, and sources that show an
astrometric excess.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with comparably bright and blue stars
\citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

\subsubsection{Summary}

Possible false-positive scenarios are as follows.

\begin{itemize}
  \item {\it Neighboring blends}.
    Ruled out to within 2 arcseconds by Phil Evans.

  \item {\it Hierarchical blends}.
    Limited by i) FEROS + Veloce RVs, and ii) speckle imaging. 
    Multicolor photometry also limits.

  At present our data do not rule out the presence of bound companion
    stars from $\approx$10--100$\,$AU, with masses in the range of
    $\approx$0.15--0.25$\,$M$_\odot$ (Figure~\ref{fig:fpscenario}).
  Roughly 2-3\% of Sun-like stars in the solar neighborhood with
    binary companions have companions in this region of parameter space
  (assuming the Raghavan+2010 CITE log-normal binary
    separation distribution, and a uniform companion mass function.)

  Companion statistics for hierarchical triples are somewhat less 
    robust, but they have been studied, for instance by CITE
    Tokovinin 2014.
  CITE Tokovinin 2014 found that 7\% of Sun-like stars are
    hierarchical triples with two companions in the compact orbit (the
    ``L$_{12}$'' configuration, rather than the ``L$_{11}$''
    configuration of say, $\alpha$~Centauri).
  A priori then, given a Sun-like primary, the probability that it is in a
    hierarchical triple configuration in which the outer orbit
    satisfies the mass and semi-major axis constraints of
    Figure~\ref{fig:fpscenario} is $\approx 7\% \times 3\% = 0.2\%$. 
  This is independent of the issue that the inner pair would require
    finely tuned orbital parameters (i) to eclipse, and (ii) to
    be so compact.

  \item {\it Background blends}.
	An argument on the a priori probability of background blends follows from
	counting statistics. Within 360 arcseconds, there are 298 T<16 stars in TIC8
	(i.e., Gaia DR2). At 2.0 arcseconds, SOAR archives dmag(I) of 6. Inside of 2
	arcseconds, we expect $\pi r^2 $ times (Nstar per sq arcsec) = 9e-3 T<16 stars.
	Any with T$\gtrsim$15 outside of 0.3 arcseconds would have been detected by
	SOAR, which brings down the expected number of possible hidden sources by a
	factor of a few.  Within 0.3 arcseconds, where SOAR gets worse than dmag(I) of
	3, we expect 2e-4 T<16 stars. So (order of magnitude), background blends would
	be a $\sim$0.1\% coincidence.
	%For the background blend to be {\it eclipsing} would require an additional
	%$\sim$2\% coincidence (CITE Kirk+2017 KEBC).
	%Combining the two probabilities yields a prior probability of $\approx$0.002\%.

\end{itemize}

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}

>>>>

The transits of \pn\ are grazing, which is a cause for concern.
Particularly for a target near the galactic plane ($b=-5.8^\circ$),
background eclipsing binaries are a major source of astrophysical
false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
follow-up data show that this and related scenarios are unlikely to
the degree that we can ``validate'' the planet, {\it i.e.}, rule that
its probability of being an astrophysical false positive is negligibly
small.  We considered this effort worthwhile because of the planet's
youth.

Section~\ref{sec:observations} describes the identification of the
candidate, and the follow-up observations collected.
Section~\ref{sec:validation} combines these data to assess the
system's false positive probability, and validates \pn\ as a planet.
Section~\ref{sec:system} presents our knowledge of the cluster
(Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
and the planet (Section~\ref{subsec:planet}).  We conclude by
discussing avenues for confirmation and improved characterization in
Section~\ref{sec:discussion}.

@@

\paragraph{Acquisition and reduction}
We observed four transits with the 0.36m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

{\bf Phil + Karen TODO: please correct as appropriate}
We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
The photometric data were calibrated and extracted using the
\texttt{AstroImageJ} software package
\citep{collins_astroimagej_2017}.  Comparison stars of similar
brightness were used to produce the final light curves, each of which
showed a roughly 4$\,$ppt dip near the expected transit time.

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B
were possible sources of blended eclipsing binary signals.
For instance, a 30\% eclipse of Star A could produce
dips with the correct depth ($\approx$0.4\%) to explain the \tn\ signal.
Star B is resolved in the ground-based images, while Star A is not.

To assess this possibility with the ground-based photometry, we
produced light curves centered on \tn\ with
circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
We did not detect any statistically significant variation in the depth
of the transits with aperture size.
Two lines evidence rule out Star B as the eclipsing source:
first, the transits
were detected in the smallest apertures.
Second, we made light curves with $2.1''$ apertures centered on Star B,
and they did not show the transit.

To assess the possibility of Star A as the eclipsing body,
we created light curves with a custom set of circular apertures
with radii of $2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
east of \tn.  We did not detect any variation of the transit depth
along this line of light curves, as would be expected if Star A were
the eclipse host.  The apertures east of \tn\ are particularly
constraining, as they exclude over 90\% of the flux from Star A.
The eclipse on Star A would therefore need to be excessively deep to
produce the observed eclipse depth.
We take this as evidence that \tn\ is the source of the transit signal
to within $\approx2.0''$.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		\label{fig:fpscenario}
	}
\end{figure*}

Validating a transiting planet means statistically arguing that
the data are much more likely to be caused by a planet than by other
astrophysical false positives. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the data must be explained by a planet, for instance through
combined photometric transits and a radial velocity mass measurement.

Assuming the eclipse is localized to the target star, potential false positive scenarios
include eclipses of a background binary (BEB), eclipses of a
hierarchical system bound to the primary star (HEB), and the possibility
that the eclipses are simply caused by a stellar companion,
rather than a planetary one (EB).

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
We proceed by describing each constraint in detail, and then present a
statistical calculation using \texttt{VESPA}
\citep{morton_efficient_2012} to demonstrate that the probability \tn\
is an astrophysical false positive is small enough to consider it
validated.

\subsection{Constraints on False Positive Scenarios}
\label{subsec:fp_constraints}

@@

For box-shaped transits, this argument can be
extended to even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
However, since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

\subsubsection{Speckle Imaging}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
possible bound companions, we used the
\citet{baraffe_evolutionary_2003} models for sub-stellar mass objects
and the MIST isochrones for stellar mass objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, to ensure that companions
would be at a plausible state of contraction.

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
assumed that all soruces had blackbody spectra.  While this is
a simplification, the custom instrumental bandpasses prevented a fully
consistent stellar evolutionary calculation.  Using the theoretical
stellar parameters and the measured transmission functions
\citep{tokovinin_ten_2018}, we then calculated the apparent magnitudes
of stellar companions of different masses, and interpolated
to produce the scale shown on the upper-right in
Figure~\ref{fig:fpscenario}.

@@

HEB and to a lesser extent BEB scenarios can be limited
by color photometry.
In the absense of color photometry, the most plausible HEB scenarios for TOI
837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
These eclipses are redder than eclipses of the G0V \tn.
Observations that the transit depth does not decrease
going to blue bands can therefore rule out these scenarios.

@@

The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
point-source detections from imaging, and sources that show an
astrometric excess.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with stars of similar brightness and color
\citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

% 151 T<15.1 stars within 360 arcseconds
% 298 T<16.0 stars within 360 arcseconds
The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends, and {\it iii)} the eclipses are
caused by neighboring stars outside $\approx 2''$.  The only scenario
not formally ruled out is a background eclipsing binary.  A simple
(fallacious) argument on the a priori probability of background blends
follows from counting statistics.  The local density of $T<15.1$ stars
around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
not excluded by the SOAR HRCam contrast curve, for a randomly selected
star we would expect $1.0\times10^{-4}$ potential $T<15.1$
contaminants, which appears small.

The reason the above statement is an insufficient argument against
BEBs is that \tn\ is not a randomly selected star---it was selected
because it shows eclipses.  Given a foreground star that shows
eclipses, the probability of a background star being present is much
greater than for an arbitrary foreground star.  The relevant
populations need to be modelled at the Monte Carlo level.  We opt to
use \texttt{VESPA} to perform this population modelling
\citep{morton_efficient_2012,vespa_2015}.

\texttt{VESPA} calculates the false positive probability for a transit
signal as
\begin{equation}
  {\rm FPP} = 1 - P_{\rm pl},
\end{equation}
where in our case the probability that the signal comes from a planet,
$P_{\rm pl}$, is given by
\begin{align}
  P_{\rm pl} = 
  \frac{
    \mathcal{L}_{\rm pl}\pi_{\rm pl}
  }{
    \mathcal{L}_{\rm pl}\pi_{\rm pl} + \mathcal{L}_{\rm BEB}\pi_{\rm BEB}
  },
\end{align}
where $\mathcal{L}_i$ is the model likelihood for the planet and BEB
scenarios, and $\pi_i$ is the model prior.  The terms labelled as
``BEB'' usually include other false positive scenarios (HEBs and EBs),
but our followup data have excluded these possibilities.  The priors
are evaluated using a combination of galactic population synthesis
\citep{girardi_star_2005}, binary star statistics
\citep{raghavan_survey_2010}, and specific planet occurrence rates
\citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
evaluated by forward-modelling a representative population of
eclipsing bodies for model class, in which each population member has
a particular trapezoidal eclipse depth, total duration, and ingress
duration.  The likelihood is then calculated by multiplying the
probability distribution function of simulated population's shape
parameters with the posterior probability of the actual observed
eclipse shape.

% results from 20200624_simple_fpp_weak_sec 
We ran \texttt{VESPA}\footnote{We used
\texttt{VESPA-0.6} and \texttt{isochrones-1.2.2}.}, and directly
incorporated our constraints of the SOAR $I$-band contrast curve and a
non-detection of secondary eclipses with a depth set at roughly twice
the limits from the SPOC vetting report (0.1\%).  We verified that
changing the secondary eclipse depth limit did not significantly
affect the results.  We set the maximum aperture radius at $2''$,
based on our ground-based photometry.  Incorporating the constraints
from Figure~\ref{fig:fpscenario}, our nominal false positive
probability analysis excluded EB and HEB scenarios.  This yielded a
FPP of 0.21\% for \pn, sufficient for formal validation as a
planet \citep{morton_efficient_2012}.  We did not incorporate our constraint that \tn\ is not
double-lined, which rules out an additional portion of BEB parameter
space.  Had we not acquired multicolor ground-based photometry, and
been unable to exclude HEB scenarios, the FPP would have risen to 8\%.
However, since the transits are achromatic
(Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
rule out HEB scenarios.

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
